Describing demographic models is hard

### 2020-05-20 paper.tex
Updated papers affected.

\jkcomment{do we want to estimate how
many times it was copied? A quick search on github suggests around 30
times]} \dncomment{I like this as a rough metric, like ``the number of copies
is unknown, but we found x copies on github''}

It was used in a number of publications
~\citep{martin2017human,albers2020dating,kelleher2019inferring,tong2020population,hubisz2019mapping,
overcast2019integrated,zhou2018popdemog,pfaffelhuber2020choose}

>>>>

It was used in a number of publications
~\citep{martin2017human,albers2020dating,kelleher2019inferring,tong2020population,
overcast2019integrated,zhou2018popdemog,pfaffelhuber2020choose}
